\section{Conclusions}

With the design and technical aspects of our project worked out, we are confident that we
can achieve our goal of helping the musician in their battle against writer's block by
creating a portable MIDI controller that can give the musician suggestions. We love having
the opportunity to use AI to help people, rather than to replace them. By helping the
musician complete their work, rather than generate entirely new works, the music will
retain the heart and soul of human creativity. We believe by providing creative assistance
we will help struggling musicians continue pursuing music when they would have otherwise
given up on their musical endeavors.

While there are other products that provide AI assisted music suggestions, we believe that
none of them provide the accessibility that our device will provide. As a standalone
device, this can be given to students or people who lack the computer skills to use a full
fledged DAW on a computer. With the simple DAW-like interface we provide, they will be
able to focus on the music without getting lost in technical details. This will also help
those who are already familiar with modern music production, by providing them with a
device they can use whenever they're stuck on a melody. The music they create on the
device can be imported to the computer when they are done, making the device useful beyond
just educational purposes.

With the research we have done over the past few months, we are in a great position to
make this project a reality. Initially, the prospect of creating this device was daunting,
with several unknowns and unfamiliar technology. But after conducting the research and
going through the design process, we have a sense of clarity and we know that we will be
able to accomplish our goals. We have started prototyping, beginning with setting up the
Raspberry Pi, prototyping the DAW user interface, and experimenting with AI. We are happy
with our technical progress up to this point and will continue develop the project to its
conclusion.

With this document, we have shown that we have considered the legal implications, broader
impacts, worked out the specifications and requirements, conducted thorough research,
worked out the design and implementation details. We have a list of equipment, a budget,
and a list of progress milestones to hold us accountable towards the project's completion.
We hope to have demonstrated with our document that our team has an understanding for what
work needs to be done and a development process to guide us there.