\section{Division of Labor}

\subsection{Software}

There are three primary components to our software: the AI, the DAW, and the backend. As such, the
workload has been divided amongst section leaders based on specialization. Jorge, who expressed
early interest in researching the Magenta AI model and has an academic background in machine
learning, was assigned head of AI development. Sam, who is the most experienced among the software
team in music production, led the development of the DAW. Mason, who spear-headed the Raspberry Pi
trials in early development, was placed at the head of backend development. The team member
assigned section leader was not necessarily responsible for carrying the majority of their
section's workload, but instead the responsibility of section leader was to make executive
decisions on the direction in which their section would proceed. Additionally, section leaders
were to coordinate with other section leaders to ensure each section's external needs were met.

This method of localized leadership was employed to maximize group synergy. Often in group
projects there can be difficulty working in parallel because each individual may have a slightly
different vision as to how the end product should work, creating friction when the work of
individuals has to eventually be compiled into a single product. Resolving these issues can become
a diplomatic problem. Having a single executive voice for each component centralizes the design
so that everyone can adhere to the same expectations.
