\section{Project Overview}
\subsection{Function of the Project}

The final product of this project should serve as a music production and music
education tool. The keyboard itself will allow the user to interactively experiment with
writing melodies, and the autofill feature will assist in expanding the user’s capability.
For music production it can kickstart the writing process, allowing a smooth and
constant flow of ideas and creativity, thereby boosting the productivity of the user.
For music education it can, through demonstration, teach stylistic patterns and
structures that the user can mimic in their own writing to create a similar sound.

The product should also simply serve as a tool of convenience. Musical practitioners often find
that it can be inconvenient to even begin a music writing or practice session, because a lot of the
necessary equipment is cumbersome or complex, requiring time to transport and set up. Smaller
instruments such as the ukulele are enjoyed particularly for their simplicity and mobility, because
it makes spontaneous bouts of music more achievable. The MIDI Autofill keyboard should fill a
similar niche in the music production community by providing more simplified functionality to a
synthesizer production set up in exchange for ease of learning and ease of use.

\subsection{Design Criteria}

Aside from achieving base functionality, there are few requirements regarding the
product’s design. Its keys should be aesthetically and structurally reminiscent of a
piano, to make for more intuitive use. Additionally, the visualization of the melody in
the DAW should follow the horizontal bar format seen in most standard MIDI editors.

The standalone design makes music production more convenient, as producers often have to have
several devices connected to each other as well as to their own power sources to have complete
utility. Because this is a key benefit of the MIDI Autofill Keyboard, our features should be
designed to enhance that mobility. A small, light-weight body will allow the user to transport it
easily. Low dependency on external power sources will also expand the variety of use by not
requiring a nearby outlet.

\subsection{Constraints}
\label{sec:constraints}

The primary constraint of this project will be hardware. Both the AI model and Digital
Audio Workstation will need to be operating without the assistance of external
processing power. Additionally, we hope to make this product affordable. To meet
these needs, we will need to strike a balance between the complexity of the software
and the capabilities of decently priced hardware.

Other constraints include budget and time. Because this project is slotted for the spring and
summer semesters, it will have to take place over a more condensed timeline. On top of that, the
team will experience limited contact in the interest of public health in the current state of the
COVID-19 pandemic. Understanding these factors, the scope of this project has been designed for
flexibility. We ensured that the minimum viable product is within an acquirable skill set, so that
 it may be achieved quickly and with few complications. At the same time, we have an expansive list
  of optional features that would improve function and enhance the technical level of the project
  if we have the time to implement them. With this structure, we have confidence in our ability to
  produce a working model within our time constraints even during restrictive circumstances but
  also plenty of room to exercise a higher level of technical achievement if time permits.

\input{legalethicalandprivacy.tex}

\input{broaderimpact.tex}
